```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)


``` library(tidyverse)
library("dplyr") 
 
```{r setup, include=FALSE}
knitr::opts_cunk$set(echo=TRUE)
source("Netflix_Subscriber_Count.R")
``` 
##Chart 3: Bar Chart
```{r netflix_barchart, echo = FALSE}
netflix_barchart
```

source("C:/Users/medha/Documents/info201/project-group-8-section-ae/source/tv_shows_graph.R")

shows_plot_america
```
  
# Chart  
```{r}
library(tidyverse)
library("dplyr")

library(knitr)
netflix_df <- read.csv("all-weeks-countries.csv")
View(netflix_df)


aggregated_table <- netflix_df %>% 
  filter(country_name == "United States") %>% 
  #Only contain relevant information (i.e., only select some columns of interest)
  #Have well formatted (i.e., human readable) column names (so you'll probably have to change them)
  select("Content type" = category, "Name" = show_title,  cumulative_weeks_in_top_10) %>% 
  #Be intentionally sorted in a meaningful way
  arrange("Top 10 week" = as.Date("Top 10 week", "%d-%m-%Y")) %>% #most recent
  #Round any quantitative values so they are displayed in a manner that isn't distracting <- n/a
  group_by(Name) %>% #so there are no duplicates
  mutate(cumulative_weeks_in_top_10 = sum(cumulative_weeks_in_top_10)) %>% 
  arrange(desc(cumulative_weeks_in_top_10))
aggregated_table <- distinct(aggregated_table)
View(aggregated_table)
kable(aggregated_table)
```

