 ```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("Netflix_Subscriber_Count.R")
``` 
## Chart 3: Bar Chart

```{r netflix_barchart, echo = FALSE}
netflix_barchart
```

_PURPOSE:_ 
The purpose of the chart is to highlight the growth of Netflix’s subscriber count over the years. (Quarter 1 2013 - Quarter 3 2022) This shows an economic growth that the company follows which will help us further our scope of data that we have included in our project to ultimately support our claim that Netflix has had a major socioeconomic impact on the world today. It’s hard to disagree with this claim purely based off of the sheer growth and volume of subscribers which we can see in the chart above. 


  
# Chart  
```{r}
library(tidyverse)
library("dplyr")

library(knitr)
netflix_df <- read.csv("all-weeks-countries.csv")
View(netflix_df)


aggregated_table <- netflix_df %>% 
  filter(country_name == "United States") %>% 
  #Only contain relevant information (i.e., only select some columns of interest)
  #Have well formatted (i.e., human readable) column names (so you'll probably have to change them)
  select("Content type" = category, "Name" = show_title,  cumulative_weeks_in_top_10) %>% 
  #Be intentionally sorted in a meaningful way
  arrange("Top 10 week" = as.Date("Top 10 week", "%d-%m-%Y")) %>% #most recent
  #Round any quantitative values so they are displayed in a manner that isn't distracting <- n/a
  group_by(Name) %>% #so there are no duplicates
  mutate(cumulative_weeks_in_top_10 = sum(cumulative_weeks_in_top_10)) %>% 
  arrange(desc(cumulative_weeks_in_top_10))
aggregated_table <- distinct(aggregated_table)
View(aggregated_table)
kable(aggregated_table)
```


