---
title: "Impact of Netflix on Human Connections"
author: "Lasya Suravajhela, Medha Rawat, Heena Vahora"

date: "11/09/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("/Users/heenavahora/Documents/info201/project-group-8-section-ae/docs/Summary_info.r")
```
# Dynamic Paragraph
TEST `r summary_info$num_observations`
Top_10_Netflix_weekly:
`r top_10_netflix_weekly_dataset`

In the first data set, we were able to find a list of films and TV shows that stayed the most viewed on Netflix in different countries through for multiple weeks. We found that in the film, `r movie_that_stayed_10_on_netflix_longest` was the film that stayed on Netflix's top 10 most viewed movie for the longest time and found `r show_that_stayed_10_on_netflix_longest` to be the TV show's that stayed on the top 10 most viewed for the longest time. 


In the second data set, the data shows different Netflix's subscription fees in different countries, we found that `r country_with_lowest_fee_on_netflix_subscription` to have the lowest subscription fee of the basic package. But in `r country_with_highest_fee_on_netflix_subscription` they are the countries with the highest basic Netflix package fees.


In the third data set, we are able to see the stocks of Netflix over the past 19 years, we could `r number_dates_collected_from_02_21` number of dates. With this information, we are able to find out why and how Netflix became the number one streaming platform.


## What is this file for?

* This file will eventually become your project report for **P02: Exploratory Data Analysis**. Specifically, you will write rmarkdown to report your exploratory data analysis.

* Please see Canvas for more details.

## ACCESSING THE /source DIRECTORY
### Example 1: Source some code and run a function

```{r}
library(tidyverse)
library("dplyr")

library(knitr)
netflix_df <- read.csv("all-weeks-countries.csv")
View(netflix_df)


aggregated_table <- netflix_df %>% 
  filter(country_name == "United States") %>% 
  #Only contain relevant information (i.e., only select some columns of interest)
  #Have well formatted (i.e., human readable) column names (so you'll probably have to change them)
  select("Content type" = category, "Name" = show_title,  cumulative_weeks_in_top_10) %>% 
  #Be intentionally sorted in a meaningful way
  arrange("Top 10 week" = as.Date("Top 10 week", "%d-%m-%Y")) %>% #most recent
  #Round any quantitative values so they are displayed in a manner that isn't distracting <- n/a
  group_by(Name) %>% #so there are no duplicates
  mutate(cumulative_weeks_in_top_10 = sum(cumulative_weeks_in_top_10)) %>% 
  arrange(desc(cumulative_weeks_in_top_10))
aggregated_table <- distinct(aggregated_table)
View(aggregated_table)
kable(aggregated_table)
```

